---
title: "Simple document"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
auther: Xinran Sun
date: 2021-09-16
---

```{r}
library(tidyverse)
```

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

Let's write a new code chunk.

This code chunk imports the `tidyverse`, creates a data frame, and makes a histogram

```{r new_code_chunk}

set.seed(1234)
plot_df = 
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1 + 2 * x + rnorm(1000)
  )

ggplot(plot_df, aes(x = x)) + geom_histogram()

```

# Practice 1

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r learning assessment}
library(tidyverse)
set.seed(12)

learning_df = tibble(
    vec_numeric = rnorm(500, mean = 1),
    vec_logic = vec_numeric > 0,
    vec_abs_numeric = abs(vec_numeric))

ggplot(learning_df, aes(x = vec_abs_numeric)) + geom_histogram()
```


